### 2014-07-28 Projects/Spartanburg_2014/Report/Spartanburg_2014.tex
Documentation/Reports: Minor style edit
Spartanburg 2014: Add fuel data

\subsection{Construction}
\label{sec:Construction}

\section{Fuel Load}

@@

\chapter{Acknowledgements}
\label{chap:Acknowledgements}

>>>>

\section{Construction}
\label{sec:Construction}

\section{Fuel Load}
\label{sec:Fuel_Load}

\begin{sidewaystable}[!ht]
\centering
\caption{Fuel masses}
\begin{tabular}{llcc}
\hline\noalign{\smallskip}
Item                         &  Material Description             &  Dimensions (m)            &  Mass (kg)  \\
\noalign{\smallskip}\hline\noalign{\smallskip}
% 3-seat Legacy Sofa         &  491 Brawley                      &  1.96 m x 0.86 m x 0.89 m  &  56.2 kg    \\
%   Cushion (left)           &  Cotton w/ inner springs          &                            &  4.06 kg    \\
%   Cushions (center)        &  Cotton w/ inner springs          &                            &  4.56 kg    \\
%   Cushions (rear)          &  Cotton w/ inner springs          &                            &  4.16 kg    \\
% 2-seat New Sofa            &  491 Brawley                      &  1.59 m x 0.91 m x 0.86 m  &  33.3 kg    \\
%   Cushion (seat)           &                                   &  0.56 m x 0.61 m x 0.14 m  &  1.6 kg     \\
%   Cushion (rear)           &  0.71 m at top, 0.58 m at bottom  &  Varies x 0.53 m x 0.20 m  &  2 kg       \\
3-seat Brown Sofa            &  302 College (front room)         &  2.24 m x 1.02 m x 0.91 m  &  61.0 kg    \\
2-seat Purple Stripe Sofa    &  302 College (front room)         &  1.57 m x 0.97 m x 0.86 m  &  82.0 kg    \\
3-seat Black Pine Leaf Sofa  &  302 College (front room)         &  2.08 m x 0.86 m x 0.86 m  &  51.0 kg    \\
Blue/Brown Chair             &  302 College (front room)         &  0.97 m x 0.81 m x 0.97 m  &  46.4 kg    \\
2-seat Floral Sofa           &  302 College (rear room)          &  1.68 m x 0.91 m x 0.91 m  &  34.5 kg    \\
2-seat Blue Plaid Sofa       &  302 College (rear room)          &  1.63 m x 0.97 m x 0.91 m  &  39.8 kg    \\
3-seat Yellow Sofa           &  302 College (rear room)          &  2.13 m x 0.91 m x 0.71 m  &  48.3 kg    \\
3-seat Floral Sofa           &  302 College (rear room)          &  2.29 m x 0.91 m x 0.91 m  &  48.0 kg    \\
3-seat New Sofa              &  289 College (front room)         &  2.13 m x 0.91 m x 0.91 m  &  43.0 kg    \\
Blue Chair                   &  289 College (middle room)        &  0.91 m x 0.91 m x 0.91 m  &  25.3 kg    \\
3-seat Floral Sofa           &  289 College (sprinkler room)     &  2.24 m x 1.02 m x 1.02 m  &  81.2 kg    \\
Floral Chair                 &  289 College (sprinkler room)     &  1.02 m x 1.02 m x 1.02 m  &  36.3 kg    \\
\noalign{\smallskip}\hline
\end{tabular}
\label{tab:Fuel_Masses}
\end{sidewaystable}

@@

\chapter{Acknowledgments}
\label{chap:Acknowledgments}
